A Dependently Typed Multi-Stage Calculus

### 2019-08-29 text/formal-defnition.tex
Fix Remark on QPercent.

\paragraph{Remark:}
\AI{Comments on \QPercent}
Without \QPercent, however, it would not be possible
to compose this function code with another piece of code
$v$ of type, say, \(\TW_\gamma \text{Vector }5\) because
\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are
syntactically different types.
% : \(\TB_\gamma (\TBL_\gamma (\text{vadd}\ 5\ \gamma)\ v\ v)\).
Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
reduction does not match the operational behavior of the CSP operator
in implementations.  However, as an equational system for multi-stage
programs, the rule \QPercent makes sense.

>>>>

\paragraph{Remark:}
When this function is composed with another piece of code $v$ of type, say,
\(\TW_\gamma \text{Vector }5\), \QPercent plays an essential role; that is,
\(\text{Vector }5\) and \(\text{Vector }(\%_\beta 5)\) are syntactically
different types but \QPercent enables to equate one with another.
Interestingly, Hanada and Igarashi~\cite{Hanada2014} rejected the idea of
reduction that removes $\%_\alpha$ when they developed \LTP{}, as such
reduction does not match the operational behavior of the CSP operator in
implementations. However, as an equational system for multi-stage programs,
the rule \QPercent makes sense.
